\documentclass{thesisreport}


\begin{document}

 \include{thesisfront}  
 
  \section*{Abstract}
   
  Humanoid robots are made as mirror to the humans. Consequently, the humanoid motion is also expected to be real as 
  human and it is natural to use human motion as an input to generate humanoid motion like a child learning from recogniting
  an action and imitating. This process in robots is called motion imitation and there are several challenges posed 
  due to kinematics and dynamics of the robot over the past decades. Although the work on the kinematic challenges is 
  actively improving and notably better than dynamics, it allows the robot only to move and imitate slow actions. 
  For the fast paced motions, \textit{momentum} gets build up and needs dynamics to be taken into account. Due to the 
  differences in redundancy between humanoid robots and humans, real-time imitation in humanoid robots while keeping 
  balance and support changes is still an challenging problem that need to be addressed.

  ~
  
  On this research, motion retargetting or the motion imitation based on dynamic balance and support with dynamic filtering 
  is implemented on humanoid robot \textit{NAO v5}, from Aldebaran Robotics. The imitation will be carried out 
  online using marker-based motion capture suit from \textit{Xsens}, specifically \textit{Xsens MVN Analyze} system.
  
  ~
  
  The captured motion from the inertial suit will be preprocessed for its representation in operational space and will be 
  scaled to the robot's dimensions. From this scaled motion, for this thesis, a set of actions are taken and will be addressed
  for the balance problem in \textit{NAO} robot. The joint, CoM and the ZMP data of the human actor will be mapped to the robot
  using the scaling function directly. To ensure the stability and to keep up the speed with the human actor, an additional 
  dynamic filter and multi-inverted pendulum based posture control will be implemented. 
 
 \newpage
 
 \section*{Acknowledgements}
 
 I would first like to thank my thesis advisor Dr Sophie Sakka for her motivation and opportunity for the thesis topic.
 Her experience, knowledge and continuous advicess have allowed me to become a better researcher and have ultimately made 
 this thesis possible. I am specifically grateful to the members in \textit{Robots! Association} for their support and providing 
 a very friendly environment during my thesis period. 

 ~
 
I would also like to thank Dr Olivier Kermorgant and Christine Chevallereau for accepting to be members of the jury, for their 
interest in my work and for their feedback on the thesis.

~

Finally, my deepest thanks go out to my parents for their constant support, advice, love and help not only during the development 
of this thesis, but throughout all of my life. Thanks for always being there when I most needed it, in spite of the distance; thanks
for all the encouragements at all times; thanks for all the beliefs I was always taught. And, overall, thanks God for the life and 
for always giving me the strength to keep forward despite all the difficulties.

\newpage
 
 
\section*{Notations}
    \begin{tabular}{p{3cm}p{10cm}}
        $x$ & Pose State Vector \\
        $q$ & Joint State Vector \\
        $r_i$ & position vector of body $i$ \\
        $m_i$ & mass of body $i$ \\
        $M$ & Total mass of the robot \\
        $\dot{q}$ & Joint Velocity Vector \\
        $\ddot{q}$ & Joint Acceleration Vector \\
        $\xi$ & generalized velocity vector \\
        $\tau$ & Generalized torque \\
        $M(\ddot{q})$ & Generalized Inertial Matrix of Robot \\
        $c(q, \dot{q})$ & Vector of Coriolis, Centrifugal and Gravity \\
        $I_i$ & Inertia matrix of body $i$ \\
        $\mathbf{g}$ & Gravity vector \\
         & \\
        $P_{CoM}$ & Position of CoM of the robot \\
        $P_{CoM_i}$ & Position of CoM of body $i$ \\
        $P_{ZMP}$ & Position of ZMP \\

        & \\

        $\mathcal{F}_i$ & Frame representation of body $i$ respecting M-DH \\
        $\mathcal{R}_i$ & Local coordinate system of body $i$ \\
        
        & \\
        



    \end{tabular}

\newpage

\section*{Abbreviations}

\begin{tabular}{p{3cm}p{15cm}}
CoM & Centre of Mass \\
DoF & Degrees of Freedom \\
ZMP & Zero Moment Point \\
OSID & Operational Space Inverse Dynamics \\
QP & Quadratic Programming \\
HQP & Hierrachical Quadratic Programming \\
eHQP & Equality-constrained Hierrachical Quadratic Programming \\
iHQP & Inequality-constrianed Hierrachical Quadratic Programming \\
M-DIP & Multi- Double Inverse Pendulum Model \\
SoT & Stack of Tasks \\
MVNX & Xsens-specific XML format \\
UDP & User Datagram Protocol \\



\end{tabular}

 \newpage
 
 \tableofcontents

 \listoffigures
 
\listoftables
 

 
 \include{introduction.tex}
\include{state_of_the_art.tex}
\include{dynamcis_based_imitation.tex}
\include{task_specification.tex}
\include{experimental_setup.tex}
\include{implementation.tex}
\include{conclusion.tex}
 
 
 
 % switch to A-B-C chaptering
 \appendix	
 
 
 \addcontentsline{toc}{chapter}{Bibliography}
 
 \bibliography{biblio}
 
 
 
 
\end{document}
